Replicating Sutton's TD($\lambda$) Algorithm

### 2019-06-01 project_1/paper.tex
Reorganizing folders to commit to GT server
Adding to GT server

\author{
  Carlos Souza\\
  %Department of Computer Science\\
  Georgia Institute of Technology\\
  São Paulo, SP, Brazil \\
  \texttt{souza@gatech.edu} \\
}

@@

% keywords can be removed
\keywords{Reinforcement learning \and Temporal-difference (TD) learning \and Markov reward process}

@@

\subsection{Random Walk}
\label{subsec:randomwalk}
Sutton (1988) illustrates TD methods with a random-walk example, one of the simplest dynamic systems.
A bounded random walk is a Markov Reward Process.
The episodes always start in the middle state $D$.
At each time step, the walk moves to the neighbor state, either left or right, with equal probability.
The episode ends when walk reaches either extreme states $A$ or $G$.
If termination happens by reaching the extreme right ($G$), environment provides a reward of +1;
all the other rewards are zero.

\begin{figure}[t]
    \includegraphics[scale=0.3]{./images/random_walk.eps}
    \centering
    \caption{A bounded random walk generator used in Sutton's original paper.
    All episodes start in state $D$.
    At each time step, walk has equal probability of either moving left or right.
    Episode ends when walk reaches either $A$ or $G$.
    In case of episode terminating in $G$, +1 reward is received;
    otherwise, reward is zero.}
    \label{fig:1}
\end{figure}

A typical episode terminating in the extreme right might be the following state-reward sequence: $D, 0, C, 0, D, 0, E, 0, F, 0, G, 1$.
An example of a walk ending in the extreme left might be: $D, 0, C, 0, B, 0, A, 0$.
This MRP is undiscounted ($\gamma = 1$);
therefore, the true value of each state is the probability of terminating on the extreme right by starting from that specific state.
Thus, the true values from all states, from $A$ to $G$ respectively, are

\begin{equation}
    v_{true} = \Bigg[0, \frac{1}{6}, \frac{2}{6}, \frac{3}{6}, \frac{4}{6}, \frac{5}{6}, 1\Bigg]
    \centering
\end{equation}

>>>>

\author{
  Carlos Souza\thanks{Latest Git hash: DO NOT FORGET TO INCLUDE LATEST GIT HASH}\\
  %Department of Computer Science\\
  Georgia Institute of Technology\\
  São Paulo, SP, Brazil \\
  \texttt{souza@gatech.edu} \\
}

@@

% keywords can be removed
\keywords{Reinforcement learning \and Temporal-difference (TD) learning \and Markov reward process}
%\githash{DO NOT FORGET TO INCLUDE LATEST GIT HASH}

@@

\subsection{Random Walk}
\label{subsec:randomwalk}
Sutton (1988) illustrates TD methods with a random-walk example, one of the simplest dynamic systems.
A bounded random walk is a Markov Reward Process.
The episodes always start in the middle state $C$.
At each time step, the walk moves to the neighbor state, either left or right, with equal probability.
The episode ends when walk reaches either extreme states ($A$'s left or $E$'s right).
If termination happens by reaching the extreme right, environment provides a reward of +1;
all the other rewards are zero.

\begin{figure}[t]
    \includegraphics[scale=0.3]{./images/random_walk2.eps}
    \centering
    \caption{A bounded random walk generator used in Sutton's original paper.
    All episodes start in state $C$.
    At each time step, walk has equal probability of either moving left or right.
    Episode ends when walk reaches either extreme left or right.
    In case of episode terminating in extreme right, +1 reward is received;
    otherwise, reward is zero.}
    \label{fig:1}
\end{figure}

A typical episode terminating in the extreme right might be the following state-reward sequence: C, 0, B, 0, C, 0, D, 0, E, 0, extreme-right (terminal), 1.
An example of a walk ending in the extreme left might be: C, 0, B, 0, A, 0, extreme-left (terminal), 0.
This MRP is undiscounted ($\gamma = 1$);
therefore, the true value of each state is the probability of terminating on the extreme right by starting from that specific state.
Thus, the true values from all states, from $A$ to $E$ respectively, are

\begin{equation}
    v_{true} = \Bigg[\frac{1}{6}, \frac{2}{6}, \frac{3}{6}, \frac{4}{6}, \frac{5}{6}\Bigg]
    \centering
\end{equation}
